Object Categorization based on RGBD data

### 2013-10-20 Disseration/architecture.tex
aa

		\subsubsection{Input/Output operations}	
		Additional functionality have to be provided in the field of input/output operations. Before any processing can be done each image have to be read into memory. Both batch inference and estimation are dataset dependant. What I mean by this is that a previously compiled database have to be accessible. The inference, on the other hand, is meant to be used in a production environment i.e. with a Kinect connected only. While the OpenNI Grabber framework from the PointCloud Library is essentially what is required for the inference, a little more elaboration has to be done on the demands of the estimation and batch inference environments. The two third party datasets used in the project have different formats and need to be tackled separately. The B3DO object dataset contains multiple objects in a single image. The locations of the images are available in xml files, while rgb and depth data are stored in separate files, 8-bit 3 channell jpeg and 16 bit one channel png respectively. Single objects have to be extracted from both pictures using the provided annotations and point cloud have to be build. The Zhang's dataset contain single objects. The rgb data is stored in 8 bit 3 channel jpegs and csv files contains euclidean coordinates of every rgb pixel. Both databases contain objects' labels that have to be loaded separately.

@@

	The described functionality can be achieved in the following way. The utilisation of Object Oriented Programming (OOP) can lead to production of modular, flexible and extensible software. Using C++ as the language of choice can result in high efficiency. The excellent metaprogramming tools provided by the C++ language help minimise the length of resulting hand-written code.

>>>>

		\subsubsection{Input/Output operations}	
		Additional functionality have to be provided in the field of input/output operations. Before any processing can be done each image have to be read into memory. Both batch inference and estimation are dataset dependant. What I mean by this is that a previously compiled database have to be accessible. The inference, on the other hand, is meant to be used in a production environment i.e. with a Kinect connected only. While the OpenNI Grabber framework from the PointCloud Library is essentially what is required for the inference, a little more elaboration has to be done on the demands of the estimation and batch inference environments. The two third party datasets used in the project have different formats and need to be tackled separately. The B3DO object dataset contains multiple objects in a single image. The locations of the images are available in xml files, while rgb and depth data are stored in separate files, 8-bit 3 channel jpeg and 16 bit one channel png respectively. Single objects have to be extracted from both pictures using the provided annotations and point cloud have to be build. The Zhang's dataset contain single objects. The rgb data is stored in 8 bit 3 channel jpegs and csv files contains euclidean coordinates of every rgb pixel. Both databases contain objects' labels that have to be loaded separately.

@@

	The described functionality can be achieved in the following way. The utilisation of Object Oriented Programming (OOP) can lead to production of modular, flexible and extensible software. Using C++ as the language of choice can result in high efficiency. The excellent meta-programming tools provided by the C++ language help minimise the length of resulting hand-written code.

### 2013-10-20 Disseration/experiments.tex
aa

\section{Experimental Setup}
	Thanks to the configurability of the programme the majority of experiments were run in a batch processing mode. That is a script in bash was written that allowed running multiple tests in series without any maintenance from the user. In a single series of tests any parameters could be modified or any data processing algorithm could be exchanged. All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz cpu, 8 Gb of RAM and a nVidia M540 GPU.

@@

	\begin{figure}[!ht]
	\centering	
	\includegraphics[width=.75\textwidth]{figs/desc_b3do}
	\caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
	\label{fig:desc_b3do}
	\end{figure}

	The figure \ref{fig:desc_b3do} shows highest accuracy obtained with the tested descriptors on the B3DO dataset. FPFH scored the best result, even tough it is an approximate and theoretically the least precise of all evaluated descriptors. On the other hand, the PFHRGB scored better than PFH. It does not surprise, since the colour information is believed to have discriminative value.

>>>>

\section{Experimental Setup}
	Thanks to the configurability of the programme the majority of experiments were run in a batch processing mode. That is a script in bash was written that allowed running multiple tests in series without any maintenance from the user. In a single series of tests any parameters could be modified or any data processing algorithm could be exchanged. All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz CPU, 8 GB of RAM and a nVidia M540 GPU.

@@

	\begin{table}[!ht]
	\centering	
	\includegraphics[width=.25\textwidth]{figs/desc_b3do}
	\caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
	\label{tab:desc_b3do}
	\end{table}

	The figure \ref{tab:desc_b3do} shows highest accuracy obtained with the tested descriptors on the B3DO dataset. FPFH scored the best result, even tough it is an approximate and theoretically the least precise of all evaluated descriptors. On the other hand, the PFHRGB scored better than PFH. It does not surprise, since the colour information is believed to have discriminative value.

### 2013-10-20 Disseration/introduction.tex
aa

	%Discriminative vs Generative approach
	%Overview of algorithms: kNN, logistic regression, SVM, NN, PGM, Naive Bayes
	To classify means to, given a set of categories, produce a category label for a given set of features \cite{ponce2011cv}. Many problems might not seem like classification problems and image categorisation is one of them. Images are too complex to be processed by any classifier directly. We can think that there are too many details, too many aspects that decide whether a picture fits into a category or not. But it turns out that many problems can be abstracted in such a way that they become pure classification problemd. One such abstraction for photographs or point clouds is the Bag of Words model. Classifiers can be two-class classifiers (e.g. binary) or multi-class classifiers. It is a common practice to build multi-class classifiers from binary ones, however. The most popular classifiers are: k-Nearest Neighbours, Logistic Regression, Na\`ive Bayes and Support Vector Machine.

@@

	\subsection{OpenCV}
	Considerably more mature, the OpenCV library is yet another great image processing library. A multitude of methods implemented in both C (OpenCV 1.x) and C++ (OpenCV 2.x) allows for production of fully functional image processing or computer vision application with this single library. There are many machine learning mechanisms as well. Among them one can find kMeans, Gausian Mixture Model, Na\`ive Bayes or a Support Vector Machine. Some of the more demanding in terms of computational power are parallelized with Threading Building Blocks (TBB). A module exploiting powers of the nVidia's CUDA technology exists in order to enhance computation even more.

@@

	Multiple RGBD datasets were created. The purpose of authors of the vast majority of them were to provide a benchmark for tasks of tracking or instance-level object recognition. Others have small number of categories or very few examples in every category. Unfortunately, the most are not fit for the object classification problem.
	The RGB-D object dataset from the University of Washington \cite{dataset_washington} would be perfect, if not for the fact that it consists of video sequences. A technology like Kinect Fusion \cite{KinectFusion} makes it relatively easy to build a detailed 3D model (a point cloud or a mesh) from such data. The only problem is in the computational cost of this method and actions required to gather such data --- in a real setting a mobile robot would have to circle an object. Two datasets are used are for the purpose of this paper. The first one is the Berkely 3D Object dataset \cite{B3DO} and the second one is a dataset compiled by Zhang \emph{et al} at the University of Tokyo \cite{zhangcategory}. The datasets are going to be abbreviated as B3DO and Tokyo datasets respectively

	\subsection{Berkely 3D Object Dataset}
	\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/b3do_dataset}
	\caption{Berkely 3D Object Dataset. The figure comes from \cite{B3DO}}
	\label{fig:b3do}
	\end{figure}

	The Berkely 3D Object dataset was specifically designed for the purpose of object classification. It consists of cluttered images in indoor environment. There are around 50 classes with more than 20 examples in each of them. RGBD data is provided as pairs of images. There are 8 bit RGB jpeg pictures and 16 bit png files containing depth data in millimetres. Images are densely labelled --- for every pair of images there is an xml with annotations. Every annotation is comprised of a category label, bounding box coordinates and object's orientation.

>>>>

	%Discriminative vs Generative approach
	%Overview of algorithms: kNN, logistic regression, SVM, NN, PGM, Naive Bayes
	To classify means to, given a set of categories, produce a category label for a given set of features \cite{ponce2011cv}. Many problems might not seem like classification problems and image categorisation is one of them. Images are too complex to be processed by any classifier directly. We can think that there are too many details, too many aspects that decide whether a picture fits into a category or not. But it turns out that many problems can be abstracted in such a way that they become pure classification problems. One such abstraction for photographs or point clouds is the Bag of Words model. Classifiers can be two-class classifiers (e.g. binary) or multi-class classifiers. It is a common practice to build multi-class classifiers from binary ones, however. The most popular classifiers are: k-Nearest Neighbours, Logistic Regression, Na\`ive Bayes and Support Vector Machine.

@@

	\subsection{OpenCV}
	Considerably more mature, the OpenCV library is yet another great image processing library. A multitude of methods implemented in both C (OpenCV 1.x) and C++ (OpenCV 2.x) allows for production of fully functional image processing or computer vision application with this single library. There are many machine learning mechanisms as well. Among them one can find kMeans, Gaussian Mixture Model, Na\`ive Bayes or a Support Vector Machine. Some of the more demanding in terms of computational power are parallelized with Threading Building Blocks (TBB). A module exploiting powers of the nVidia's CUDA technology exists in order to enhance computation even more.

@@

	Multiple RGBD datasets were created. The purpose of authors of the vast majority of them were to provide a benchmark for tasks of tracking or instance-level object recognition. Others have small number of categories or very few examples in every category. Unfortunately, the most are not fit for the object classification problem.
	The RGB-D object dataset from the University of Washington \cite{dataset_washington} would be perfect, if not for the fact that it consists of video sequences. A technology like Kinect Fusion \cite{KinectFusion} makes it relatively easy to build a detailed 3D model (a point cloud or a mesh) from such data. The only problem is in the computational cost of this method and actions required to gather such data --- in a real setting a mobile robot would have to circle an object. Two datasets are used are for the purpose of this paper. The first one is the Berkeley 3D Object dataset \cite{B3DO} and the second one is a dataset compiled by Zhang \emph{et al} at the University of Tokyo \cite{zhangcategory}. The datasets are going to be abbreviated as B3DO and Tokyo datasets respectively

	\subsection{Berkeley 3D Object Dataset}
	\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/b3do_dataset}
	\caption{Berkeley 3D Object Dataset. The figure comes from \cite{B3DO}}
	\label{fig:b3do}
	\end{figure}

	The Berkeley 3D Object dataset was specifically designed for the purpose of object classification. It consists of cluttered images in indoor environment. There are around 50 classes with more than 20 examples in each of them. RGBD data is provided as pairs of images. There are 8 bit RGB jpeg pictures and 16 bit png files containing depth data in millimetres. Images are densely labelled --- for every pair of images there is an xml with annotations. Every annotation is comprised of a category label, bounding box coordinates and object's orientation.
